Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-13 analysis/paper/paper.Rmd
Fix linebreaks in Author contributions

Plant pathology is not alone in the lack of reproducibility and with the close-nature of data and code.
In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture, [@Smith2018; @Arnaud2020; @Stacey2022].
However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.

@@

Efforts to annotate structured raw data (FAIR -- Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
The metadata further define the resource that has been made available allowing for discovery and use by other interested parties.
That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.

>>>>

Plant pathology is not alone in the lack of reproducibility and with the close-nature of data and code.
In response to this, other related disciplines have published guides or started communities to promote and support tools and methods that promote good practices that lead to open and reproducible research.In entomology @Wittman2020 published "A Guide and Toolbox to Replicability and Open Science in Entomology", which documented both the benefits and drawbacks of an open and reproducible workflow.
Weed scientists started a community to promote openness in the discipline, Open Weed Science, which stated that they valued, "open access knowledge-sharing as a strategy to enhance reproducibility within our discipline", but the website is no longer available and the Twitter account, \@OpenWeedSci, appears to be inactive when viewing the account as of October 2022 [@OpenWeedScience2021].
@SerradaCruz2019 proposed a framework for capturing provenance of data-centric agronomic experiments using an R-based workflow, 'RFlow', which would allow reuse of R scripts using generic workflows and saving data and metadata to web repositories that other researchers and referees can browse using Web interfaces.
@Kool2020 evaluated the reproducibility of on-farm experiments in Africa, finding that often the experimental design was difficult or impossible to reproduce from the publication.
More broadly within agricultural research, articles have been published highlighting the advantages of, need for and how to publish FAIR data in agriculture [@Smith2018; @Arnaud2020; @Stacey2022].
However, we were unable to find any quantification of the reproducibility of any of these related disciplines as we have done here.

@@

Efforts to annotate structured raw data, make it FAIR (Findable, Accessible, Interoperable and Re-usable) [@Wilkinson2016] and fully document the analysis using open-source code which are deposited in public repositories and can be run by anyone following the download of data and code.
Making the raw data FAIR means providing proper metadata, a clear description of what the resource contains, how it can be used and other attributes about it that help users understand it.
The metadata further define the resource that has been made available allowing for discovery and use by other interested parties.
That is, proper cataloguing and descriptions of the computational materials and data enable others to easily find and understand what the materials are.
Properly constructed metadata allow for interoperability by allowing both humans and machines to understand what the materials are that are included in the resources and make use of them more easily.
Metadata also protects the resource and its future availability by tracking the resource's lineage, describing the resources physical characteristics and behavior so that it can be replicated using future technologies.
That is, without metadata, the data are not FAIR and the computational materials lose value by not having good documentation.
